---
title: "p8105_hw6_yz4990"
author: "Yucheng Zhao"
date: "2024-12-02"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
```


The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.
## Problem 1.
```{r}
homi_df = read_csv("./data/homicide-data.csv", 
                   na = c("NA", "Unknown", ""), 
                   ) |> 
  janitor::clean_names() |> 
  mutate(
    city_state = paste(city, state, sep = ", ")
    ) |> 
  filter(city != "Dallas", 
         city != "Phoenix",
         city != "Kansas City", 
         city != "Tulsa") |> 
  filter(victim_race == "White" | victim_race == "Black") |> 
  drop_na(victim_age) |> 
  mutate(victim_age = as.numeric(victim_age))


```



# Problem 2. 
```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```




```{r}

```





